Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem

### 2015-12-04 acta_manuscript.tex
working on poincare section detail

\section{Introduction}\label{sec:introduction}
% MOTIVATION FOR LOW THRUST ORBITAL TRANSFER 
Designing spacecraft trajectories is a classic and ongoing topic of research.
%With the current fiscal constraints there is an increased focus on technologies with a critical impact on mass.
Optimal expenditure of onboard propellant is critical to allowing a mission to continue for a longer period of time or to enable the launch of a less massive spacecraft.
Electric propulsion systems offer a much greater specific impulse than chemical systems and are able to operate for extended periods of time.
However, these electric propulsion systems typically have much less thrust than their chemical counterparts and therefore must operate over longer durations in order to impart the desired momentum change.
Recent developments in miniature electric propulsion offer the potential for new research opportunities for small spacecraft~\cite{haque2013}.
With reduced development intervals and decreased launch costs, small satellites have gained increased attention as a cost effective means of scientific and technologic development. 
The merger of small satellites with miniature electric propulsion enables inexpensive and responsive missions requiring large changes in orbital energy or extended mission lifespan.
With the potential for more demanding missions, even greater importance is placed on the mission design to ensure that optimal trajectories satisfy mission requirements. 
In addition, non-Keplerian orbits and multi-body dynamics have been shown to allow for a much greater range of potential missions at a reduced energy cost~\cite{koon2000}.
Future space missions are increasing in complexity and will require new classes of orbits that are not possible via the traditional patched-conic approach~\cite{ross2006,gomez2001}.
Optimally combining the dynamical structure of the three-body problem with low-thrust propulsion systems is vital for future mission success.

@@

To achieve these objectives, computational geometric optimal control techniques are applied. 
We generalize the previous work of determining orbital transfers using invariant manifolds~\cite{koon2000}.
We incorporate the effects of continuous low thrust propulsion to enable departure from the system dynamics and enable increased transfer opportunities.
The dynamics of the three-body system are derived from the discrete Lagrangian, which approximates the integral of the continuous time Lagrangian over a fixed discrete step.
Application of the discrete Euler-Lagrange equations, or the discrete Legendre transform, results in the discrete equations of motion.
This discrete update map, or variational integrator, shares the same geometric properties of the continuous time system and exhibits much better energy behavior than the traditional integration methods, especially over long transfer durations with small magnitude control inputs.
A discrete optimal control problem is formulated from the discrete equations of motion.
This approach, where explicit discretization occurs prior to optimization,  is in contrast to the typical method, where the equations of motion are implicitly discretized during the optimization procedure.
Formulating the problem in this manner results in more stable and accurate optimal solutions. 
In indirect methods the optimal control problem is expressed as a two-point boundary value problem.
Optimal solutions are generally sensitive to small variations in the initial multipliers.
As a result, the numerical stability of sensitivity derivatives is critical to accuracy and computational performance. 
The use of geometric integrators, which do not suffer the numerical dissipation of conventional integration methods, results in a more robust and efficient solution.

@@

\section{Planar Circular Restricted Three Body Problem}\label{sec:pcrtbp}
The system model is based on the planar circular restricted three body problem~(PCRTBP).
The Earth is assumed to be the more massive primary, \( m_1 \), while the Moon is the second, smaller primary \( m_2\).
The equations of motion are developed in a rotating reference frame which allows for much greater insight into the structure of the dynamics.
The \( \hat{e}_1 \) axis is directed along the vector from the Earth to the Moon.
The \( \hat{e}_2 \) axis lies in the orbital plane and is orthogonal to \( \hat{e}_1 \).
The rotating reference frame is centered at the system barycenter.
It is assumed that the \(\left( \hat{e}_1, \hat{e}_2\right)\) frame rotates with a constant angular velocity equal to the mean motion of the Moon.
Following convention, the system is also non-dimensionalized by the characteristic mass, length, and time~\cite{koon2000}.
As a result, the system can be characterized by a single mass parameter \( \mu \),
\begin{equation}
	\mu = \frac{m_2}{m_1+m_2} \, .
	\label{eq:mass_param}
\end{equation}
The larger primary, \(m_1\), is located at \( \left(  -\mu , 0 \right)\) and the smaller \( m_2\) is located at \( \left( 1-\mu , 0 \right)\), while the spacecraft is located at \( x \hat{e}_1 + y \hat{e}_2 \).
In the rotating reference frame the Lagrangian is given by
\begin{equation}
	L = \frac{1}{2} \left( \left( \dot{x} -y \right)^2 + \left( \dot{y} + x \right)^2 \right) + \frac{1-\mu}{r_1} + \frac{\mu}{r_2}\, ,
	\label{eq:lagrangian}
\end{equation}
where the distance \( r_1, r_2 \in \R \) of the spacecraft to each primary is defined in rotating coordinates as
\begin{align}
	r_1 &= \sqrt{\left( x + \mu\right)^2 + y^2}\, , \\
	r_2 &= \sqrt{\left( x - 1 + \mu\right)^2 + y^2}\, .
	\label{eq:distances}
\end{align}
Application of the Euler-Lagrange equations results in following equations of motion defined in the rotating reference frame
\begin{align}
	\ddot{x} - 2 \dot{y} + \deriv{U}{x} &= u_x \, ,\nonumber \\
	\ddot{y} + 2 \dot{y} + \deriv{U}{y} &= u_y \, ,
	\label{eq:cont_eom}
\end{align}
where the effective potential \( U\) is defined as
\begin{equation}
	U = \frac{1}{2} \left( x^2 + y^2\right) + \frac{1-\mu}{r_1} + \frac{\mu}{r_2}\, ,
	\label{eq:eff_pot}
\end{equation}
and the control inputs are defined as \( u_x \text{ and } u_y \in \R \).
The state is defined as \( \bar{x} = \begin{bmatrix}\bar{r} &\bar{v} \end{bmatrix}^T\) with \(\bar{r} \in \R^{2\times1}\) and \(\bar{v} \in \R^{2\times1}\) representing the position and velocity with respect to the system barycenter, respectively.
The equations of motion may be rewritten in state space form as
\begin{equation}\label{eqn:cont_dyn}
	\left[\begin{array}{c} \dot{\bar{r}} \\ \dot{\bar{v}} \end{array} \right] = 
	\left[ \begin{array}{c} \bar{v} \\ A \bar{v} + \nabla U + \bar{u}(t) \end{array} \right] = f\left( t,x, u\right) \, ,
\end{equation}
where the matrix \( A \) and psuedo gravitational potential gradient \( \nabla U\) are
\begin{equation}\label{eq:A_mat}
	A = \left[ \begin{array}{ccc} 0 & 2 & 0 \\ -2 & 0 & 0 \\ 0 & 0 & 0 \end{array} \right] \, ,
\end{equation}
\begin{equation} \label{eq:grav_pot}
	\nabla U = \left[ \begin{array}{c} x - \frac{ \left(1 - \mu\right) \left(x + \mu\right)}{r_1^3} - \frac{\mu \left( x - 1 + \mu \right)}{r_2^3} \\
											y - \frac{ \left(1 - \mu\right) y}{r_1^3} - \frac{\mu y}{r_2^3} \\
											- \frac{ \left(1 - \mu\right) z}{r_1^3} - \frac{\mu z}{r_2^3}\end{array}\right]
					= \left[\begin{array}{c} U_x \\ U_y \\ U_z\end{array} \right] \, .
\end{equation}

@@

% technical definition of manifold and some equations
Invariant manifolds serve as a higher dimensional generalization of the concept of seperatrices from linear systems to the case of nonlinear systems. 
To compute these manifolds first one must determine an appropriate periodic orbit. 
The process of differential correction and numerical continuation are used to determine a periodic orbit with a desired energy level. 
Let the trajectories of the equations of motion defined in~\cref{eqn:cont_dyn} be defined by the flow map \( \phi(t;\vec{x}_0) \) originating from the initial condition \( \vec{x}(t_0) = \vec{x}_0 \) and and a periodic orbit denoted by \( \gamma\).
The invariant manifolds: 
\begin{align*}
	W^s ( \vec{x}_0 ) &= \braces{ \vec{x} : \phi(t;\vec{x}_0) \to \gamma \text{ as } t \to \infty} \\
	W^u ( \vec{x}_0 ) &= \braces{ \vec{x} : \phi(t;\vec{x}_0) \to \gamma \text{ as } t \to -\infty} 
\end{align*}
are the set of trajectories that asymptotically depart or approach a periodic orbit.
For the nonlinear system~\cref{eqn:cont_dyn} or~\cref{eq:discrete_eoms}, we can determine the state transition matrix \( \Phi \) along the periodic orbit, from \( 0 \to T\), by numerical integration of the variational equations.
In the neighborhood of the periodic orbit \( \gamma \), the tangent spaces to the stable and unstable manifolds are provided by the generalized eigenspaces \( E^s \) and \( E^u \) of the linearization \( A = \D f(\vec{x}_0) \) where \( \vec{x}_0 \) is on the periodic orbit.
The eigenvectors of the monodromy matrix, \( M = \Phi(T) \), serve to locally approximate the directions of the stable and unstable manifolds. 
A perturbation in the direction of the unstable eigenvector, outside the unit circle, is used to generate an initial condition on the unstable manifold. 
Similarly, a perturbation in the direction of the stable eigenvector, inside the unit circle, is used to generate an initial condition on the stable manifold. 
Each periodic orbit has two stable and unstable manifold sets associated with both a postive or negative perturbation along the respective eigenvector.
This idea is illustrated by~\cref{fig:invariant_manifold}.
\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{invariant_manifold}
	\caption{Stable and unstable manifold of a periodic orbit\label{fig:invariant_manifold}}
\end{figure}

% introduce \Poincare section theory and math
Another useful technique in the analysis of the free motion of dynamical systems is that of the \Poincare section.
The \Poincare section is the intersection of a periodic orbit of a dynamical system with a lower dimensional sub-space transverse to the flow.
This allows for greater insight into the stability and dynamics of periodic solutions of dynamic system. 
Points are drawn as the periodic solution intersects the \Poincare section.
Great insight and structure into the dynamical system is typically available through use of \Poincare section.
For example, \cref{fig:poincare_sections} shows the intersections of the invariant manifolds of~\cref{fig:invariant_manifolds} with the \Poincare sections defined by the black line segments.
The \Poincare section and the Jacobi integral reduce the state space from four to two dimensions for the planar three-body problem~\cite{koon2001}.
This greatly eases the design process and allows for a simple planar visualization of the intersection of the invariant manifolds.
Intersecting states are easy to determine and allow for transfers between invariant manifolds.
\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{poincare_map}
	\caption{\Poincare map\label{fig:poincare_map}}
\end{figure}
% intro to how you can determine intersection on a poincare section for transfers
The intersection of the invariant manifolds on a \Poincare section is central to determining the desired control-free trajectory.
However, the results previously developed are highly case specific and difficult to generalize to arbitrary transfers.
Also, these results are based on control-free trajectories which rely on the underlying structure of the three-body system.
In addition, transfer orbits along an invariant manifold require large time of flights which may be undesirable for time critical missions.
The addition of low-thrust propulsion offers the potential of reduced transit times and the ability to depart from the free motion trajectory to allow for increased transfer opportunities. 
In this work, an optimal control problem is formulated to generate a reachable set of the spacecraft.
The reachable set is computed on an appropriate \Poincare section and is used to design an appropriate transfer trajectory.

% detail on how invariant manifolds can be used for transfers (example of koon work)
In this way, it is possible to design trajectories that intersect the invariant manifolds and connect widely separated regions of the state space. 
\Cref{fig:invariant_manifolds} shows some of the tubes, projected from the phase space onto the configuration space, associated with \( L_1 \) and \( L_2 \) periodic orbits in the Earth-Moon system. 
This technique has been heavily investigated in Reference~\citenum{koon2000}, applied to operational missions in Reference~\citenum{koon1999}, and applied to potential multi-moon orbiter missions in Reference~\citenum{tanaka2011}.
In addition, much recent work has focused on potential return missions to the Moon~\cite{zanzottera2012,campagnola2012,mingotti2011,ozimek2010a,mingotti2009}.
\begin{figure}
     \centering
        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\columnwidth]{U1_Manifolds}
                \caption{U1 Manifolds}
                \label{fig:u1_manifolds}
        \end{subfigure}%
        ~
        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\columnwidth]{U1_poincare}
                \caption{U1 Section}
                \label{fig:u1_poincare}
        \end{subfigure}
        \caption{Invariant manifold}
	\label{fig:u1}
\end{figure}

>>>>

\section{Introduction}\label{sec:introduction}
% MOTIVATION FOR LOW THRUST ORBITAL TRANSFER 
Designing spacecraft trajectories is a classic and ongoing topic of research.
%With the current fiscal constraints there is an increased focus on technologies with a critical impact on mass.
Optimal expenditure of onboard propellant is critical to allowing a mission to continue for a longer period of time or to enable the launch of a less massive spacecraft.
Electric propulsion systems offer a much greater specific impulse than chemical systems and are able to operate for extended periods of time.
However, these electric propulsion systems typically have much less thrust than their chemical counterparts and therefore must operate over longer durations in order to impart the desired momentum change.
Recent developments in miniature electric propulsion offer the potential for new research opportunities for small spacecraft~\cite{haque2013}.
With reduced development intervals and decreased launch costs, small satellites have gained increased attention as a cost effective means of scientific and technologic development. 
The merger of small satellites with miniature electric propulsion enables inexpensive and responsive missions requiring large changes in orbital energy or extended mission lifespan.
With the potential for more demanding missions, even greater importance is placed on the mission design to ensure that optimal trajectories satisfy mission requirements. 
In addition, non-Keplerian orbits and multi-body dynamics have been shown to allow for a much greater range of potential missions at a reduced energy cost~\cite{koon2011}.
Future space missions are increasing in complexity and will require new classes of orbits that are not possible via the traditional patched-conic approach~\cite{ross2006,gomez2001}.
Optimally combining the dynamical structure of the three-body problem with low-thrust propulsion systems is vital for future mission success.

@@

To achieve these objectives, computational geometric optimal control techniques are applied. 
We generalize the previous work of determining orbital transfers using invariant manifolds~\cite{koon2011}.
We incorporate the effects of continuous low thrust propulsion to enable departure from the system dynamics and enable increased transfer opportunities.
The dynamics of the three-body system are derived from the discrete Lagrangian, which approximates the integral of the continuous time Lagrangian over a fixed discrete step.
Application of the discrete Euler-Lagrange equations, or the discrete Legendre transform, results in the discrete equations of motion.
This discrete update map, or variational integrator, shares the same geometric properties of the continuous time system and exhibits much better energy behavior than the traditional integration methods, especially over long transfer durations with small magnitude control inputs.
A discrete optimal control problem is formulated from the discrete equations of motion.
This approach, where explicit discretization occurs prior to optimization,  is in contrast to the typical method, where the equations of motion are implicitly discretized during the optimization procedure.
Formulating the problem in this manner results in more stable and accurate optimal solutions. 
In indirect methods the optimal control problem is expressed as a two-point boundary value problem.
Optimal solutions are generally sensitive to small variations in the initial multipliers.
As a result, the numerical stability of sensitivity derivatives is critical to accuracy and computational performance. 
The use of geometric integrators, which do not suffer the numerical dissipation of conventional integration methods, results in a more robust and efficient solution.

@@

\section{Planar Circular Restricted Three Body Problem}\label{sec:pcrtbp}
The system model is based on the planar circular restricted three body problem~(PCRTBP).
The Earth is assumed to be the more massive primary, \( m_1 \), while the Moon is the second, smaller primary \( m_2\).
The equations of motion are developed in a rotating reference frame which allows for much greater insight into the structure of the dynamics.
The \( \hat{e}_1 \) axis is directed along the vector from the Earth to the Moon.
The \( \hat{e}_2 \) axis lies in the orbital plane and is orthogonal to \( \hat{e}_1 \).
The rotating reference frame is centered at the system barycenter.
It is assumed that the \(\left( \hat{e}_1, \hat{e}_2\right)\) frame rotates with a constant angular velocity equal to the mean motion of the Moon.
Following convention, the system is also non-dimensionalized by the characteristic mass, length, and time~\cite{koon2011}.
As a result, the system can be characterized by a single mass parameter \( \mu \),
\begin{equation}
	\mu = \frac{m_2}{m_1+m_2} \, .
	\label{eq:mass_param}
\end{equation}
The larger primary, \(m_1\), is located at \( \left(  -\mu , 0 \right)\) and the smaller \( m_2\) is located at \( \left( 1-\mu , 0 \right)\), while the spacecraft is located at \( x \hat{e}_1 + y \hat{e}_2 \).
In the rotating reference frame the Lagrangian is given by
\begin{equation}
	L = \frac{1}{2} \left( \left( \dot{x} -y \right)^2 + \left( \dot{y} + x \right)^2 \right) + \frac{1-\mu}{r_1} + \frac{\mu}{r_2}\, ,
	\label{eq:lagrangian}
\end{equation}
where the distance \( r_1, r_2 \in \R \) of the spacecraft to each primary is defined in rotating coordinates as
\begin{align}
	r_1 &= \sqrt{\left( x + \mu\right)^2 + y^2}\, , \\
	r_2 &= \sqrt{\left( x - 1 + \mu\right)^2 + y^2}\, .
	\label{eq:distances}
\end{align}
Application of the Euler-Lagrange equations results in following equations of motion defined in the rotating reference frame
\begin{align}
	\ddot{x} - 2 \dot{y} + \deriv{U}{x} &= u_x \, ,\nonumber \\
	\ddot{y} + 2 \dot{y} + \deriv{U}{y} &= u_y \, ,
	\label{eq:cont_eom}
\end{align}
where the effective potential \( U\) is defined as
\begin{equation}
	U = \frac{1}{2} \left( x^2 + y^2\right) + \frac{1-\mu}{r_1} + \frac{\mu}{r_2}\, ,
	\label{eq:eff_pot}
\end{equation}
and the control inputs are defined as \( u_x \text{ and } u_y \in \R \).
The state is defined as \( \bar{x} = \begin{bmatrix}\bar{r} &\bar{v} \end{bmatrix}^T\) with \(\bar{r} \in \R^{2\times1}\) and \(\bar{v} \in \R^{2\times1}\) representing the position and velocity with respect to the system barycenter, respectively.
The equations of motion may be rewritten in state space form as
\begin{equation}\label{eqn:cont_dyn}
	\left[\begin{array}{c} \dot{\bar{r}} \\ \dot{\bar{v}} \end{array} \right] = 
	\left[ \begin{array}{c} \bar{v} \\ A \bar{v} + \nabla U + \bar{u}(t) \end{array} \right] = f\left( t,x, u\right) \, ,
\end{equation}
where the matrix \( A \) and psuedo gravitational potential gradient \( \nabla U\) are
\begin{equation}\label{eq:A_mat}
	A = \left[ \begin{array}{ccc} 0 & 2 & 0 \\ -2 & 0 & 0 \\ 0 & 0 & 0 \end{array} \right] \, ,
\end{equation}
\begin{equation} \label{eq:grav_pot}
	\nabla U = \left[ \begin{array}{c} x - \frac{ \left(1 - \mu\right) \left(x + \mu\right)}{r_1^3} - \frac{\mu \left( x - 1 + \mu \right)}{r_2^3} \\
											y - \frac{ \left(1 - \mu\right) y}{r_1^3} - \frac{\mu y}{r_2^3} \\
											- \frac{ \left(1 - \mu\right) z}{r_1^3} - \frac{\mu z}{r_2^3}\end{array}\right]
					= \left[\begin{array}{c} U_x \\ U_y \\ U_z\end{array} \right] \, .
\end{equation}

@@

% technical definition of manifold and some equations
Invariant manifolds serve as a higher dimensional generalization of the concept of seperatrices from linear systems to the case of nonlinear systems. 
To compute these manifolds first one must determine an appropriate periodic orbit. 
The process of differential correction and numerical continuation are used to determine a periodic orbit with a desired energy level. 
Let the trajectories of the equations of motion defined in~\cref{eqn:cont_dyn} be defined by the flow map \( \phi(t;\vec{x}_0) \) originating from \( \vec{x}(t_0) = \vec{x}_0 \) and we define a periodic orbit as \( \gamma\).
The invariant manifolds: 
\begin{align*}
	W^s ( \vec{x}_0 ) &= \braces{ \vec{x} : \phi(t;\vec{x}_0) \to \gamma \text{ as } t \to \infty} \\
	W^u ( \vec{x}_0 ) &= \braces{ \vec{x} : \phi(t;\vec{x}_0) \to \gamma \text{ as } t \to -\infty} 
\end{align*}
are the set of trajectories that asymptotically depart or approach a periodic orbit.
For the nonlinear system~\cref{eqn:cont_dyn} or~\cref{eq:discrete_eoms}, we can determine the state transition matrix \( \Phi \) along the periodic orbit, from \( 0 \to T\), by numerical integration of the variational equations.
In the neighborhood of the periodic orbit \( \gamma \), the tangent spaces to the stable and unstable manifolds are provided by the generalized eigenspaces \( E^s \) and \( E^u \) of the linearization \( A = \D f(\vec{x}_0) \), where \( \vec{x}_0 \) is on the periodic orbit.
The eigenvectors of the monodromy matrix, \( M = \Phi(T) \), serve to locally approximate the directions of the stable and unstable manifolds. 
A perturbation in the direction of the unstable eigenvector, with \( \norm{\lambda} > 1 \), is used to generate an initial condition on the unstable manifold. 
Similarly, a perturbation in the direction of the stable eigenvector, with \( \norm{\lambda} < 1 \), is used to generate an initial condition on the stable manifold. 
Each periodic orbit has two stable and unstable manifold sets associated with both a positive or negative perturbation along the respective eigenvector.
This is technique of determining the invariant manifolds is graphically presented in~\cref{fig:invariant_manifold}.
\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{invariant_manifold}
	\caption{Stable and unstable manifold of a periodic orbit\label{fig:invariant_manifold}}
\end{figure}

% introduce \Poincare section theory and math
\Poincare maps are a useful tool in the analysis of the flow near periodic orbits in the three-body problem.
We let \( \Sigma \) be a hypersurface of section chosen such that all trajectories in the vicinity of a state \( q \in \Sigma \) cross \( \Sigma \) transversely and in the same direction.
A \Poincare map, \( P(q) = \phi(T;q) \), maps the state of a trajectory from one intersection to the next.
Choosing a section in this manner results in a \Poincare section as shown in~\cref{fig:poincare_map}.
This allows for greater insight into the stability and dynamics of periodic solutions of dynamic system as a fixed point on the \Poincare section corresponds to a periodic orbit while movement on the section is associate with the stability of neighboring trajectories. 
For example, \Poincare maps have been used to prove the existence of homoclinic orbits, orbits which are both forward and backward asymptotic to a single unstable periodic orbit, and heteroclinic orbits, which join different periodic orbits~\cite{conley1968,koon2000b}.
These dynamic features have been shown to play a vital role in the movement of natural bodies as well as critical for spacecraft missions~\cite{lo1997,gomez2001}.
\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{poincare_map}
	\caption{\Poincare map\label{fig:poincare_map}}
\end{figure}

% intersect invariant manifolds on poincare section
% find intersection between stable and unstable manifolds
% define the sections used in Koon2011 (placed strategically near heteroclinic points) - rotation of manifolds
Combining invariant manifolds and an appropriate \Poincare section provides a simple manner to determine trajectories which cross wide regions of the phase space.
The intersection of the invariant manifolds on a \Poincare section is central to determining the desired control-free trajectory.
However, the results previously developed are highly case specific and difficult to generalize to arbitrary transfers.
Also, these results are based on control-free trajectories which rely on the underlying structure of the three-body system.
In addition, transfer orbits along an invariant manifold require large time of flights which may be undesirable for time critical missions.
The addition of low-thrust propulsion offers the potential of reduced transit times and the ability to depart from the free motion trajectory to allow for increased transfer opportunities. 
In this work, an optimal control problem is formulated to generate a reachable set of the spacecraft.
The reachable set is computed on an appropriate \Poincare section and is used to design an appropriate transfer trajectory.

In this way, it is possible to design trajectories that intersect the invariant manifolds and connect widely separated regions of the state space. 
\Cref{fig:invariant_manifolds} shows some of the tubes, projected from the phase space onto the configuration space, associated with \( L_1 \) and \( L_2 \) periodic orbits in the Earth-Moon system. 
This technique has been heavily investigated in Reference~\citenum{koon2000}, applied to operational missions in Reference~\citenum{koon1999}, and applied to potential multi-moon orbiter missions in Reference~\citenum{tanaka2011}.
In addition, much recent work has focused on potential return missions to the Moon~\cite{zanzottera2012,campagnola2012,mingotti2011,ozimek2010a,mingotti2009}.
\begin{figure}
     \centering
        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\columnwidth]{U1_Manifolds}
                \caption{U1 Manifolds}
                \label{fig:u1_manifolds}
        \end{subfigure}%
        ~
        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\columnwidth]{U1_poincare}
                \caption{U1 Section}
                \label{fig:u1_poincare}
        \end{subfigure}
        \caption{Invariant manifold}
	\label{fig:u1}
\end{figure}
